---
output: 
  html_document:
    toc: true
    toc_depth: 3   # This sets the level of headers to include in the TOC
    toc_float: 
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(tidytext)
library(janitor)
library(readr)
library(kableExtra)
```

```{r}
data <- read_csv("results-survey615211.csv") %>% 
  filter(!(`How would you define, in your own words, a “systematic review”?`=="xx"))

Questions_groups <- read_csv("Questions_groups.csv")
```

## General public

```{r}
data_GeneralPublic<-
data %>% 
  select(starts_with(c("How familiar are you with the term systematic review",
"I am aware how systematic reviews are different from traditional literature",
"How frequently do you read or consult published systematic reviews in your field",
"I am planning to conduct systematic review in the future",
"Have you published a systematic review - e.g. in a scientific journal or as a thesis",
"I think that systematic reviews are important for advancing scientific knowledge",
"If you answered ”Strongly disagree” or ”Disagree” to the previous question, what is the reason for your answer")))
```


### Q1: How familiar are you with the term systematic review?
```{r}
Q1_data<-data %>% 
  group_by(`How familiar are you with the term systematic review?`) %>% 
  count() %>% 
  rename(name=1) %>% 
  ungroup() %>% 
  mutate(Percentage=n/sum(n))

Q1_data %>% 
  ggplot(aes(x=reorder(str_wrap(name, width = 20),-Percentage),y=Percentage))+
  geom_bar(stat="identity",fill="#d9dde7",color="#c6cad3")+
  theme_minimal()+
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

Q1_data %>% 
  mutate(Percentage=round(Percentage,2))%>% 
  arrange(-n) %>% 
  kbl() %>%   
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### Q2-Q6: Use of SRs
```{r}
data_GeneralPublic %>% 
  select(`I am aware how systematic reviews are different from traditional literature reviews.`,
         `How frequently do you read or consult published systematic reviews in your field?`,
         `I am planning to conduct systematic review in the future.`,
         `I think that systematic reviews are important for advancing scientific knowledge.`
         ) %>% 
  pivot_longer(everything()) %>% 
  group_by(name,value) %>% 
  count() %>% 
  mutate(order=case_when( ## double check here this step: there might be new entries that need to be ordered
    name=="How frequently do you read or consult published systematic reviews in your field?"&value=="I do not know"~1,
    name=="How frequently do you read or consult published systematic reviews in your field?"&value=="Rarely"~2,
    name=="How frequently do you read or consult published systematic reviews in your field?"&value=="Sometimes"~3,
    name=="How frequently do you read or consult published systematic reviews in your field?"&value=="Somewhat Often"~4,
    name=="How frequently do you read or consult published systematic reviews in your field?"&value=="Very Often"~5,
    name=="I am aware how systematic reviews are different from traditional literature reviews."&value=="Extremely"~5,
    name=="I am aware how systematic reviews are different from traditional literature reviews."&value=="Moderately"~3,
    name=="I am aware how systematic reviews are different from traditional literature reviews."&value=="Not at all"~1,
    name=="I am aware how systematic reviews are different from traditional literature reviews."&value=="Slightly"~2,
    name=="I am aware how systematic reviews are different from traditional literature reviews."&value=="Very"~4,
    name=="I am planning to conduct systematic review in the future."&value=="Agree"~4,
    name=="I am planning to conduct systematic review in the future."&value=="Disagree"~2,
    name=="I am planning to conduct systematic review in the future."&value=="Strongly Agree"~5,
    name=="I am planning to conduct systematic review in the future."&value=="Strongly Disagree"~1,
    name=="I am planning to conduct systematic review in the future."&value=="Neutral"~3,
    name=="I think that systematic reviews are important for advancing scientific knowledge."&value=="Neutral"~1,
    name=="I think that systematic reviews are important for advancing scientific knowledge."&value=="Agree"~2,
    name=="I think that systematic reviews are important for advancing scientific knowledge."&value=="Strongly Agree"~3,
  )) %>% 
  ggplot(aes(y = reorder(str_wrap(value, width = 40),order),x=n))+
  geom_bar(stat="identity",fill="#efefef",color="#cacaca")+
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        strip.background = element_rect(fill="#d9dde7",color=NA))+
  facet_wrap(.~name, scales = "free",ncol=1)
```

```{r}
ResearchersHavePublishedSRYES<- sum(data_GeneralPublic$`Have you published a systematic review - e.g. in a scientific journal or as a thesis?`=="Yes")
```

### Q7: Have you published a systematic review - e.g. in a scientific journal or as a thesis?
`r ResearchersHavePublishedSRYES` out of `r nrow(data_GeneralPublic)` researchers have answered Yes to the question 'Have you published a systematic review - e.g. in a scientific journal or as a thesis?'

### Q9-11: Have you ever conducted a systematic review? Why yes and why not?
Q10 and Q11 are multiple choice questions
```{r}
#Have you ever conducted a systematic review?
data %>% group_by(`Have you ever conducted a systematic review?`) %>% count() %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

#Why yes
data %>%
  select(starts_with("If you answered ”Yes” to the previous question, what motivated you to conduct a systematic review? ")) %>% 
  rename_with(~ gsub("If you answered ”Yes” to the previous question, what motivated you to conduct a systematic review\\?", "", .)) %>% 
  rename_with(~ gsub("\\[", "", .))%>% 
  rename_with(~ gsub("\\]", "", .)) %>%
  rename_with(~ gsub("^\\s+", "", .)) %>%
   pivot_longer(everything(), names_to = "column", values_to = "value") %>%
  group_by(column, value) %>%
  summarise(count = n()) %>% ungroup() %>% 
  mutate(keep=ifelse(column=="Other"|value=="Yes","keep","not")) %>% filter(keep=="keep"&!is.na(value)) %>% select(-keep) %>% 
  mutate(column=ifelse(column=="Other",paste0(column," - ",value),column)) %>% select(-value) %>% 
  rename(`If you answered ”Yes” to the previous question, what motivated you to conduct a systematic review?`=column) %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

#Why not
data %>%
  select(starts_with("If you answered ”No” to the previous question, what is the reason for not conducting a systematic review?  ")) %>% 
  rename_with(~ gsub("If you answered ”No” to the previous question, what is the reason for not conducting a systematic review\\?", "", .)) %>% 
  rename_with(~ gsub("\\[", "", .))%>% 
  rename_with(~ gsub("\\]", "", .)) %>%
  rename_with(~ gsub("^\\s+", "", .)) %>%
  mutate(`Not relevant to my research`=ifelse(Other=="was not yet relevant in my work","Yes",`Not relevant to my research`)) %>% 
  mutate(Other=ifelse(Other=="was not yet relevant in my work",NA,Other)) %>% 
   pivot_longer(everything(), names_to = "column", values_to = "value") %>%
  group_by(column, value) %>%
  summarise(count = n()) %>% ungroup() %>% 
  mutate(keep=ifelse(column=="Other"|value=="Yes","keep","not")) %>% filter(keep=="keep"&!is.na(value)) %>% select(-keep) %>% 
  mutate(column=ifelse(column=="Other",paste0(column," - ",value),column)) %>% select(-value) %>% 
  rename(`If you answered ”No” to the previous question, what is the reason for not conducting a systematic review?`=column) %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

### Q12-13: n SRs and timeframe
```{r}
data_SRAcademics<-
data %>% 
  filter(`Have you ever conducted a systematic review?`=="Yes") %>% 
  select(starts_with(c("How many systematic reviews have you been involved in",
"On average, how many months did it take you to perform a systematic review (from protocol writing to a first draft of a publication)",
"I have encountered problems in publishing my systematic review (i.e. rejections by journals, difficult peer review)",
"Which systematic review step(s) have you been involved in",
"There is an established process for systematic review in my group",
"In the past, have you consulted any of the following external experts to help you with the systematic review",
"What was/ were the most challenging step(s) of systematic review for you",
"Would you consider performing another systematic review",
"If you answered ”Extremely Unlikely” to the previous question, why",
"Have you ever used one of the following software or tools to support you in the systematic review",
"If you answered ”I have never used a software for systematic reviews” to the previous question, why",
"Which aspects of the systematic review software or tools do you think can be improved",
"What was the population of the systematic reviews you have performed",
"If you have answer either ”Animal studies” or ”Both”, what was the rationale behind conducting a systematic review in animal studies")))



medianSRConducted<-median(data_SRAcademics$`How many systematic reviews have you been involved in?  []`)
minSRConducted<-min(data_SRAcademics$`How many systematic reviews have you been involved in?  []`,na.rm = T)
maxSRConducted<-max(data_SRAcademics$`How many systematic reviews have you been involved in?  []`,na.rm = T)
monthsSR<-round(median(data_SRAcademics$`On average, how many months did it take you to perform a systematic review (from protocol writing to a first draft of a publication)?  []`,na.rm = T))
minMonthsSR<-(min(data_SRAcademics$`On average, how many months did it take you to perform a systematic review (from protocol writing to a first draft of a publication)?  []`,na.rm = T))
maxMonthsSR<-(max(data_SRAcademics$`On average, how many months did it take you to perform a systematic review (from protocol writing to a first draft of a publication)?  []`,na.rm = T))

```

Researchers have been involved in a median of `r medianSRConducted`, with a range of `r minSRConducted` - `r maxSRConducted`. It took of `r monthsSR` months (median) to complete a SR (from protocol writing to a first draft of a publication) (range: `r minMonthsSR` - `r maxMonthsSR`).

### Q14-16: 1. Academics who have conducted a SR
```{r fig.height=10}
data_SRAcademics %>% 
  mutate(`Would you consider performing another systematic review?`=case_when(
    `Would you consider performing another systematic review?`=="Likely"~"Agree",
    `Would you consider performing another systematic review?`=="Extremely Likely" ~"Strongly Agree",
    `Would you consider performing another systematic review?`=="Neutral"~"Neutral",
    `Would you consider performing another systematic review?`=="Extremely Unlikely"~"Strongly Disagree",
    `Would you consider performing another systematic review?`=="Unlikely"~"Disagree"
  )) %>% 
  rename(`I would consider performing another systematic review.`=`Would you consider performing another systematic review?`) %>% 
  select(`I have encountered problems in publishing my systematic review (i.e. rejections by journals, difficult peer review).`,
         `There is an established process for systematic review in my group.`,
         `I would consider performing another systematic review.`) %>% 
  pivot_longer(everything()) %>% 
  group_by(name,value) %>% count() %>% 
  pivot_wider(names_from = value,values_from = n) %>% 
  select(name,`Strongly Disagree`,Disagree,Neutral,Agree,`Strongly Agree`)  %>%
  rename("Questions"=1) %>% 
  kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### Q17-21: 2. Academics who have conducted a SR
```{r fig.width=10, fig.height=8}
data_SRAcademics %>% 
  select(starts_with(c("Which systematic review step(s) have you been involved in",
                       "What was/ were the most challenging step(s) of systematic review",
                       "Have you ever used one of the following software or tools to support you in the systematic review",
                       "Which aspects of the systematic review software or tools do you think can be improved",
                       "In the past, have you consulted any of the following external experts to help you with the systematic review"))) %>% 
  pivot_longer(everything()) %>% 
  separate(name, into = c("Question", "Group"), sep = "\\[") %>% 
  mutate(Group = gsub("\\]", "", Group)) %>% 
  filter(value != "No") %>% 
  group_by(Question, Group) %>% 
  count() %>% 
  arrange(Question, n) %>% 
  ungroup() %>% 
  ggplot(aes(y = reorder_within(Group, n, Question), x = n)) +
  geom_bar(stat = "identity", fill = "#efefef", color = "#cacaca") +
  facet_wrap(. ~ str_wrap(Question, width = 60), scales = "free", ncol = 1) +
  scale_y_reordered() + 
  theme_minimal() +
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        strip.background = element_rect(fill = "#d9dde7", color = NA))
```

### Q22-23: SR population
Multiple choice questions
```{r fig.height=10}
data_SRAcademics %>% 
  select(starts_with("What was the population of the systematic reviews you have performed")) %>% 
  rename_with(~ gsub("What was the population of the systematic reviews you have performed\\?", "", .))%>% 
  rename_with(~ gsub("\\[", "", .))%>% 
  rename_with(~ gsub("\\]", "", .)) %>%
  rename_with(~ trimws(.)) %>% 
  mutate(`Human Studies`=ifelse(`Both`=="Yes","No",`Human Studies`)) %>% 
  mutate(`Animal Studies`=ifelse(`Both`=="Yes","No",`Animal Studies`)) %>%
  pivot_longer(everything()) %>% 
  filter(value!="No") %>% 
  mutate(name=ifelse(name=="Other",paste0(name," - ",value),name)) %>% 
  group_by(name) %>% count()%>% 
    rename(`What was the population of the systematic reviews you have performed?`=name) %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


```{r fig.height=10}
data_SRAcademics %>% select(starts_with("If you have answer either ”Animal studies” or ”Both”, what was the rationale behind c")) %>% 
    pivot_longer(everything()) %>% 
    filter(value!="N/A") %>% 
    filter(value!="No") %>% 
    filter(!is.na(value)) %>% 
    mutate(name=gsub("If you have answer either ”Animal studies” or ”Both”, what was the rationale behind conducting a systematic review in animal studies\\?","",name))%>% 
  mutate(name= gsub("\\[", "", name))%>% 
  mutate(name= gsub("\\]", "", name)) %>% 
    mutate(name=trimws(name)) %>% 
  mutate(name=ifelse(name=="Other",paste0(name," - ",value),name)) %>% 
    group_by(name) %>% count() %>% 
    rename(`If you have answer either ”Animal studies” or ”Both”, what was the rationale behind conducting a systematic review in animal studies?`=name) %>% 
    kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
    
```

## Animal research/Future of SR
### Q24: Animal experimentation
```{r}
data_AnimalResearch<-
data %>% 
  select(starts_with(c("Have you performed animal experimentation in the past year",
"I am familiar with the concept of 3Rs (Replacement, Reduction and Refinement of animals in research",
"I believe systematic reviews can be a valuable alternative method to animal experimentation",
"I would be interested in attending a workshop or training session on conducting systematic reviews")))


data_AnimalResearch %>% group_by(`Have you performed animal experimentation in the past year?`) %>% count() %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### Q25-27: Animal Welfare
```{r}
data_AnimalResearch %>% 
  select(starts_with(c(
"I am familiar with the concept of 3Rs (Replacement, Reduction and Refinement of animals in research",
"I believe systematic reviews can be a valuable alternative method to animal experimentation",
"I would be interested in attending a workshop or training session on conducting systematic reviews"))) %>% 
  pivot_longer(everything()) %>% 
  group_by(name,value) %>% count() %>% 
  pivot_wider(names_from = value,values_from = n) %>% 
  select(name,Disagree,Neutral,Agree) %>% 
  rename(Questions=name) %>% 
  kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

## Demographics

### Q28-29: Gender and age
```{r}
data_demographics<-
data %>% 
  select(starts_with(c("Select your gender",
"Your age",
"Your Nationality",
"Which country do you reside in",
"At which institution(s) are you currently working (e.g., University of Zürich, Department of molecular biology)",
"Which field are you working in",
"What is the highest degree you have obtained",
"Which stage of your career are you currently pursuing")))


nFemales<-sum(data_demographics$`Select your gender.`=="Female")
medianAge<-round(mean(data_demographics$`Your age:  []`),1)
minAge<-round(min(data_demographics$`Your age:  []`),1)
maxAge<-round(max(data_demographics$`Your age:  []`),1)
sdAge<-round(sd(data_demographics$`Your age:  []`),1)
```
`r nFemales` (`r round((nFemales/nrow(data_demographics))*100)`%) of the participants were females. Median age was `r medianAge` (range: `r minAge` - `r maxAge`)

### Q33: Field of work
```{r}
data_demographics%>% 
  select(starts_with("Which field are you working in")) %>% 
  rename_with(~ gsub("Which field are you working in\\?", "", .))%>% 
  rename_with(~ gsub("\\[", "", .))%>% 
  rename_with(~ gsub("\\]", "", .)) %>% 
  pivot_longer(everything()) %>% 
  filter(value!="No") %>% 
  mutate(name=trimws(name),
         name=ifelse(name=="Other",paste0(name," - ",value),name)) %>% 
  group_by(name) %>% count() %>% 
  rename(`Which field are you working in?`=name) %>% kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### Q34-35: Career
```{r}
data_demographics %>% 
  mutate(`What is the highest degree you have obtained?`=ifelse(
    `What is the highest degree you have obtained?`=="Other",`What is the highest degree you have obtained?  [Other]`,`What is the highest degree you have obtained?`
  )) %>% 
  group_by(`What is the highest degree you have obtained?`) %>% 
  count() %>% arrange(-n) %>% 
  kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
  
data_demographics %>% 
  group_by(`Which stage of your career are you currently pursuing?`) %>% 
  count() %>% arrange(-n)%>% 
  kbl() %>%   kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```









